---
title: "Exo2_penguins"
author: "Gael Mariani"
date: "02/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data penguins

Data on __penguins__ with size measurements for three penguin species observed on island in Palmer Archipelago, size (flipper length, body mass, bill dimensions), and sex. 

```{r echo = FALSE, include = FALSE}
library(palmerpenguins)
library(tidyverse)
library(ggplot2)
library(citr)
```

```{r echo = FALSE, eval = TRUE}
penguins %>%
  head(10) %>%
  knitr::kable(format = "html", caption = "Head of the first ten lines of the __penguins__ dataset")
```  
<br/>

The dataset contains measurements on `r nrow(penguins)` individuals belonging to `r length(unique(penguins$species))` differents species. The average value of each measured traits by species is found in Table 2. 

```{r echo = FALSE, eval = TRUE}
penguins %>%
  group_by(species) %>% 
  summarise_if(is.numeric, mean, na.rm=T) %>%
  select(-"year") %>%
  knitr::kable(format = "html", caption = "Table 2: Average value by species of the bill length, the bill depth and the flipper length (millimeters) and the body mass (grams) ")
```  


## Graphic exploration
```{r echos = TRUE, message = FALSE, warning=FALSE}
penguins %>%
  select(c("species", "body_mass_g")) %>%
  ggplot() +
  geom_histogram(mapping = aes(x = body_mass_g, color = species, fill = species), 
                 alpha = 0.3, position = "identity") +
  theme_bw()
```


